Binary companions of red giant stars in \apogee\ \DR

### 2018-03-04 paper/1-catalog/twoface-catalog.tex
Implementation notes
comment change
Description of table

@@

We select a sample of stars that confidently have companions using percentiles
computed from the posterior samples in the velocity semi-amplitude parameter,
$K$.
\figurename~\ref{fig:lnK-percentiles}, shows the distribution of 1st percentiles
of $\ln K$ computed for all stars with posterior samplings from \thejoker\
(filled, blue histogram), along with the same for posterior samplings for the
null control sample (solid, dark line).
To select stars with companions, we use a cut in the 1st percentile of the $\ln
K$ samples such that $<1\%$ of the control sample is selected, i.e. our
estimated false positive rate is $<1\%$.
We use a threshold of $\ln K = 0$ to meet this constraint (vertical, dashed line
in \figurename~\ref{fig:lnK-percentiles}); \nhighK\ stars pass this cut.

@@

\tablename~\ref{tbl:} contains a subset of the \apogee\ \DR\ \texttt{allStar}
catalog information for the stars that pass the above cut and therefore likely
have companions; For brevity below, we refer to this sample as the ``high-$K$''
stars, and the complimentary sample as the ``low-$K$'' stars.
\figurename s~\ref{fig:highK-0} and \ref{fig:highK-1} show eight examples of
high-$K$ stars, i.e. stars that likely have companions, with different numbers
of visits, $N$, indicated on the panels.
\figurename s~\ref{fig:lowK-0} and \ref{fig:lowK-1} is the same for eight
low-$K$ stars, i.e. stars that either have no companions, low-mass companions,
or companions at long periods or high inclination.

@@

@@

% Notebook: HighK-unimodal
\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{highK-unimodal}
\end{center}
\caption{%
Examples of high-$K$ stars with effectively unimodal posterior samplings and
converged MCMC samplings.
Each panel shows the data (black markers), phase-folded at the period of the
posterior sample with maximum posterior probability.
Visit velocity uncertainties are shown as black error bars (these are typically
smaller than or equal to the size of the markers), and the inferred jitter as
grey, capped error bars.
Line (blue) shows the orbit compute from the posterior sample with maximum
posterior probability.
\label{fig:highK-unimodal}
}
\end{figure}

@@

% Notebook: HighK-unimodal
\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{unimodal-P-e}
\end{center}
\caption{%
TODO:
\label{fig:unimodalPe}
}
\end{figure}

@@

>>>>

% How do we run TheJoker on all of APOGEE? Run on a cluster, send batches of samples to processors because individual likelihood calls are fast
%
% How do we do MCMC? Similar issues as above, but less control because not inherently embarassingly parallel

@@

We select a sample of stars that confidently have companions using percentiles
computed from the posterior samples in the velocity semi-amplitude parameter,
$K$.
\figurename~\ref{fig:lnK-percentiles}, shows the distribution of 1st percentiles
of $\ln K$ computed for all stars with posterior samplings from \thejoker\
(filled, blue histogram), along with the same for posterior samplings for the
null control sample (solid, dark line).
To select stars with companions, we use a cut in the 1st percentile of the $\ln
K$ samples such that $<1\%$ of the control sample is selected, i.e. our
estimated false positive rate is $<1\%$.
We use a threshold of $\ln K = 0$ to meet this constraint (vertical, dashed line
in \figurename~\ref{fig:lnK-percentiles}); \nhighK\ stars pass this cut.
For brevity below, we refer to this sample as the ``high-$K$'' stars, and the
complimentary sample as the ``low-$K$'' stars.

@@

\begin{table}
    \centering
    \begin{tabular}{c | c}
    \texttt{APOGEE\_ID} & \texttt{lnK\_per\_1} \\
    \hline
    2M00000002+7417074 & -2.028 \\
    2M00000068+5710233 & -2.600 \\
    2M00000222+5625359 &  2.134 \\
    2M00000446+5854329 & -7.199 \\
    2M00000535+1504343 & -4.457 \\
    2M00000546+6152107 & -4.388 \\
    2M00000797+6436119 & -0.774 \\
    2M00000866+7122144 & -3.313 \\
    ... & ...
    \end{tabular}
    \caption{This table contains the \texttt{APOGEE\_ID} for all \nstars\ stars
    in the parent sample used in this work, for which we have posterior
    samplings in orbital parameters.
    The other column contains the 1st percentile computed over the $\ln K$
    samples for each source, \texttt{lnK\_per\_1}:
    The ``high-$K$'' sample (see \sectionname~\ref{sec:catalog-confident}) is
    defined using this column, by selecting \texttt{lnK\_per\_1 > 0}.
    }
    \label{tbl:lnK-per}
\end{table}

\tablename~\ref{tbl:lnK-per} contains a list of all stars in the parent sample
and the value of the 1st percentile over the $\ln K$ samples for each star.
\figurename s~\ref{fig:highK-0} and \ref{fig:highK-1} show eight examples of
high-$K$ stars, i.e. stars that likely have companions, with different numbers
of visits, $N$, indicated on the panels.
\figurename s~\ref{fig:lowK-0} and \ref{fig:lowK-1} is the same for eight
low-$K$ stars, i.e. stars that either have no companions, low-mass companions,
or companions at long periods or high inclination.

@@

\todo{How do we actually select these?}

@@

% Notebook: HighK-unimodal-catalog
\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{highK-unimodal}
\end{center}
\caption{%
Examples of high-$K$ stars with effectively unimodal posterior samplings and
converged MCMC samplings.
Each panel shows the data (black markers), phase-folded at the period of the
posterior sample with maximum posterior probability.
Visit velocity uncertainties are shown as black error bars (these are typically
smaller than or equal to the size of the markers), and the inferred jitter as
grey, capped error bars.
Line (blue) shows the orbit compute from the posterior sample with maximum
posterior probability.
\label{fig:highK-unimodal}
}
\end{figure}

@@

% Notebook: HighK-unimodal
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.7\textwidth]{unimodal-P-e}
\end{center}
\caption{%
TODO:
\label{fig:unimodalPe}
}
\end{figure}

@@

\todo{comment on short period shit, eccentricities}
